---
title: "Untitled"
author: "Abdellah"
date: "2/8/2018"
output: html_document
---

Libraries
```{r}
  library(purrr)
  library(readr)
  library(ggplot2)
  library(langcog)
  library(boot)
#  library(lazyeval)
  library(dplyr)
  library(tidyr)
  library(wordbankr)
  library(directlabels)
 # library(scales)
  library(stringr)
  library(lmtest)
  library(rwebppl)
  library(jsonlite)
  library(nlme)
  library(feather)
  library(broom)
  library(HDInterval)
  library(BBmisc)
  library(data.table)
  library(plyr)
```

The continuous model

```{r}

model_cont <- "

var Id = function(position, rotation){
  return {x:position.x, y:position.y};
};

//this reflection is for front/back
var Ref = function(position, rotation){
  return {x:-position.x, y:-position.y};
};

//define rotation in general
////////////////////////////

var Rot = function(position, rotation){
  var theta = rotation
  var theta_rad = theta * Math.PI * 1/180
  var rot_x= position.x*Math.cos(theta_rad)-position.y*Math.sin(theta_rad);
  var rot_y= position.x*Math.sin(theta_rad)+position.y*Math.cos(theta_rad);

  return {x:Math.round(rot_x), y:Math.round(rot_y)};
};

//define rotation for side (left-right)
var Rot_side = function(position, rotation){
  return Rot(position, 90)
}

//This rotation is for non-egocentric frame of reference 
var Rot_allo = function(position, rotation){
  return Rot(position, rotation)
}

//define composition 
var Comp = function (opr1, opr2){
  return function (position, rotation){
    opr1(opr2(position, rotation),rotation)
  }
}

//So we are learning 4 words: both front/back, left/right, and we have 8 hypotheses

var hyp_space = [ {name:'id', operation:Id, len:1}, // front
                  {name:'ref', operation:Ref, len:1}, // back
                 
                  {name:'rotSide_id', operation:Comp(Rot_side,Id), len:2}, //left ego
                  {name:'rotSide_ref', operation:Comp(Rot_side,Ref), len:2}, // right ego
                 
                  {name:'rotFrame_id', operation:Comp(Rot_allo,Id), len:2}, //front allo
                  {name:'rotFrame_ref', operation:Comp(Rot_allo,Ref), len:2}, // right allo
                 
                  {name:'rotFrame_Side_id', operation:Comp(Rot_allo, Comp(Rot_side, Id)), len:3}, //left allo
                  {name:'rotFrame_Side_ref', operation:Comp(Rot_allo, Comp(Rot_side, Ref)), len:3} //right allo

 
                ]


var hyp_names  =  map(function(hyp){
return hyp.name
}, hyp_space)

var positions = [
                 {x:-1,y:0},
                 {x:1, y:0},
                 {x:0, y:1},
                 {x:0, y:-1}
                  ];

var utterances = ['left',
                  'right',
                  'front',
                  'back'
                 ];

var rotations = [0,
                90,
                180,
                270];

var utterancePrior = Categorical({vs: utterances, ps: [1/4, 1/4, 1/4, 1/4]});
var positionPrior =  Categorical({vs: positions, ps: [1/4, 1/4, 1/4, 1/4]});
var rotationPrior =  Categorical({vs: rotations, ps: [1/4, 1/4, 1/4, 1/4]});

//Every word (e.g., 'left' , 'right') has a probability distribution over all hypotheses 
// have a different prioir for each word and each hypothesis
//let's first try different infernce for each word 

var wordPrior = function(word) { 
    var hypProbs = T.toScalars(dirichlet(ones([hyp_names.length, 1])))
    return Categorical({vs: hyp_names, ps: hypProbs})
}


//Egocentric Meaning: returns true if the word maps to the correct position  
var meaning = function(utt, position, rotation) {
    var rot_position = Rot(position, -rotation)
    return utt=='front'? (rot_position.x==0 && rot_position.y==1):
    utt=='back'? (rot_position.x==0 && rot_position.y==-1):
    utt=='left'? (rot_position.x==-1 && rot_position.y==0):
    utt=='right'? (rot_position.x==1 && rot_position.y==0):
    true
};

//Speaker: has in mind a position, and utter the corresponding word based on rotation 
var S = cache(function(position, rotation) {
  return Infer({method:'enumerate'}, function(){
    var utt = sample(utterancePrior);
    condition(meaning(utt, position, rotation));
    return utt;
  });
});


var data = input  

var alpha=data[0].alpha
var beta=data[0].beta
var myWord = data[0].word 

//Listner: hears a word, sees a rotation and try to associate it with a meaning from the space

//Do a conditional (if the word is the same )
var L1 = function(trueRotation, wordDist) {
  return Infer({method:'enumerate'}, function(){
    var rep = uniformDraw(hyp_space); //sample a representation
    var rep_opr = rep.operation
    var response =  rep_opr({x:0,y:1}, trueRotation) 
  
    factor(alpha*wordDist.score(rep.name)-beta*rep.len)
    //factor(-beta*rep.len)
    //factor(alpha*wordDist.score(rep.name)+beta*rep.len)
    return [response.x, response.y]
  });
};



var wordPost = function(word, data) {
  return Infer({method : 'MCMC', samples : 10000, burn: 2000}, function() {
    var wordDist = wordPrior(word);
    mapData({data: data}, function(datum){
      if (datum.word == word) {observe(L1(datum.rot, wordDist), [datum.x, datum.y])}
    });
    return wordDist;
  });
};


//model()
var learnData = function(size) {
  
  var step = function(data) {
    if(data.length == size) return data;
    
    var position = sample(positionPrior)
    var rotation = sample(rotationPrior)
    var utt = sample(S(position, rotation))
    
    var newDatum = {x: position.x, y: position.y, rot: rotation, word: utt}
  
  return  step(data.concat(newDatum));
    
  }
  
    step([]);
}


var model =  function () {
  var data = learnData(20)
  var hyps = map(function(w){ 
      return wordPost(w, data).MAP().val;
    }, utterances)
  return _.object(utterances, hyps);
};

//var data = learnData(10)

wordPost(myWord, data).MAP().val

"
```

```{r}
x=c(1, 1,  1, -1)
y=c(0, 0, 0, 0)
rot=c(0, 0, 0, 180)
word='right'

N = 2

input = data.frame(alpha = 2, beta = 2, x=rep(x,3), y=rep(y,3), rot=rep(rot,3), word = rep(rep(word, 4), 3)) %>% head(N)
      
post_all <- data.frame()

for (i in seq(1,2)) {
posterior <- webppl(program_file = "models/model.wppl", 
                    data = input,
                    data_var = "input")
posterior <- posterior %>%
  mutate(mcmc = i)

post_all <- bind_rows(post_all, posterior)


}

data_sum <- post_all %>%
  group_by(support) %>%
  summarise(mean = mean(prob),
            sd = sd(prob))


ggplot(post_all, aes(x=N, y=mean, col=hypothese))+
  
  geom_pointrange(aes(ymin = lower, ymax = upper), 
                  position = position_dodge(width = .1)) + 
  geom_line()+
  
  facet_grid(hypothese  ~ beta) +
  theme(aspect.ratio = 0.7, axis.text.x = element_text(angle = 90, hjust = 1))

```


```{r}

mcmc_values = data.frame()

names =  c(posterior[[1,3]][1], posterior[[1,3]][2], posterior[[1,3]][3], posterior[[1,3]][4], 
             posterior[[1,3]][5], posterior[[1,3]][6], posterior[[1,3]][7], posterior[[1,3]][8])

for (i in 1:nrow(posterior)) {
  
    line = data.frame(posterior[[i,2]][1], posterior[[i,2]][2], posterior[[i,2]][3], posterior[[i,2]][4], 
             posterior[[i,2]][5], posterior[[i,2]][6], posterior[[i,2]][7], posterior[[i,2]][8])
    
    mcmc_values = bind_rows(mcmc_values, line)

}

colnames(mcmc_values) <- names

means <- data.frame(sapply(mcmc_values, mean)) %>%
  rename(mean = sapply.mcmc_values..mean.)

means <- cbind(rownames(means), means)
rownames(means) <- NULL
colnames(means) <- c('hypothese', 'mean')


sds <- data.frame(sapply(mcmc_values, sd)) %>%
  rename(sd = sapply.mcmc_values..sd.)

sds <- cbind(rownames(sds), sds)
rownames(sds) <- NULL
colnames(sds) <- c('hypothese', 'sd')

all <- means %>%
  left_join(sds)

sapply(mcmc_values, sd) 
my_sum <- mcmc_values %>%
  sapply(mean)
  group_by(key) %>%
  summarize(mean = mean(value), 
            sd = sd(value))

```



Input data and run continuous model

-One way to represent the data: I can show only the average over the 4 positions 
```{r}

alpha_val = c(2)
beta_val = c(2)
N_val = seq(1, 12)

data_right_exp_cont = data.frame()

x=c(1,  0, -1, 0)
y=c(0, 1, 0, -1)
rot=c(0, 90, 180, 270)

x=c(1,  1, 1, 0)
y=c(0, 0, 0, -1)
rot=c(0, 0, 0, 270)

word='right'

for (alpha in alpha_val){
  for(beta in beta_val){
    for(N in N_val){
      
      input = data.frame(alpha = alpha, beta = beta, x=rep(x,3), y=rep(y,3), rot=rep(rot,3), word = rep(rep(word, 4), 3)) %>% head(N)
      
      post_all <- data.frame()
      for (i in seq(1,10)) {
      posterior <- NULL
      while (typeof(posterior)=="NULL") {
       posterior <- webppl(model_cont, 
                    data = input,
                    data_var = "input") 
      }
      
      posterior <- posterior %>%
        mutate(mcmc = i)
      
      post_all <- bind_rows(post_all, posterior)
      
      }
      
    
      learning <- post_all %>%
        mutate(word = word, 
               alpha= alpha,
               beta = beta,
               N=N)
      
      data_right_exp_cont = bind_rows(data_right_exp_cont, learning)
    }
    
  }
  
}


alpha_val = c(2)
beta_val = c(6, 8)
N_val = seq(1, 12)

data_front_exp_cont = data.frame()

x=c(0, -1, 0, 1)
y=c(1, 0, -1, 0)
rot=c(0, 90, 180, 270)

x=c(0, 0, 0, 1)
y=c(1, 1, 1, 0)
rot=c(0, 0, 0, 270)

word='front'

for (alpha in alpha_val){
  for(beta in beta_val){
    for(N in N_val){
      
      input = data.frame(alpha = alpha, beta = beta, x=rep(x,3), y=rep(y,3), rot=rep(rot,3), word = rep(rep(word, 4), 3)) %>% head(N)
  
      
      post_all <- data.frame()
      for (i in seq(1,10)) {
      posterior <- NULL
      while (typeof(posterior)=="NULL") {
       posterior <- webppl(model_cont, 
                    data = input,
                    data_var = "input") 
      }
      
      posterior <- posterior %>%
        mutate(mcmc = i)
      
      post_all <- bind_rows(post_all, posterior)
      
      }
      
    
      learning <- post_all %>%
        mutate(word = word, 
               alpha= alpha,
               beta = beta,
               N=N)
      
      data_front_exp_cont = bind_rows(data_front_exp_cont, learning)
    }
    
  }
  
}

```



```{r}

feather::write_feather(data_front_exp_cont, "moreEgoInput_front.feather")

data_explore  <- data_front_exp_cont  #%>%
  #filter(word == "right")#,
         #beta < alpha |  beta == alpha) 
  
  
data_explore$support <- mapvalues(data_explore$support, 
                                     from = c("id", "ref",  
                                              "rotSide_id","rotSide_ref",
                                              "rotFrame_id","rotFrame_ref",
                                              "rotFrame_Side_id","rotFrame_Side_ref"),
                                     to = c("front_ego", "back_ego", 
                                            "left_ego", "right_ego", 
                                            "front_allo", "back_allo", 
                                            "left_allo", "right_allo"))

data_explore$support = factor(data_explore$support, levels = c("front_ego", "back_ego", "left_ego", "right_ego", "front_allo", "back_allo", "left_allo", "right_allo"))

right_alpha <- ggplot(data_explore, aes(x=N, y=prob))+
  
  geom_point()+
  geom_smooth()+
  
  facet_grid(support  ~ beta) +
  theme(aspect.ratio = 0.7, axis.text.x = element_text(angle = 90, hjust = 1))



```


Ideas for how to present the data

-Posterior probability as a function of the data 
->I should see that front-back converge first (with the posterior probability ->1)
->Left-right converge second (posteririor ->)
->Ego centric probability first, Allo-centric second
-Left-right, and front-back converge at the same time 

Implement the continuous version 

explore the behavior of the model under:
-Different values of alpha, and beta (especially beta)
-Different distribution of the input (the convergence is delayed if the initial input is dominated by ago-centric representation).


Input to the model should be 
-Alpha, beta
-Number of training data
-orientation 0 vs [0,180] vs. [0, 90, 180, 270]

Rotation 0
-The siplest case, No ambiguity, words are associated with fixed spatial positions

Rotation 0, 180
-left-right data is orthogonal to front-back, ambiguity is within the symmetry only 

Rotation 0, 90, 180, 270
-Maximal ambiguity, all 4 words can be confused

In terms of the input
The input can also make the problem more or less easy
-If we start with non-overlapping input? 


Preliminary results
-We have interesting interaction between the parameter that penalizes length and the number of data needed to converge (altough the coarse granularity of the space of probabilities does not allow us to see if there is a little advantage to accurate (longest) representation).
input:
-Number of datapoints
-The values of alpha/beta




Eexperimenting here

```{r}
alpha_val = c(2)
beta_val = c(1, 1.75)
N_val = seq(1,8)

#Right/Left
#############

data_right_exp = data.frame()

x=c(1, 0, -1, 0)
y=c(0, 1, 0, -1)
rot=c(0, 90, 180, 270)
word=c('right', 'right', 'right', 'right')

for (alpha in alpha_val){
  for(beta in beta_val){
    for(N in N_val){
      
      input = data.frame(alpha = alpha, beta = beta, x= rep(x,3), y = rep(y,3), rot = rep(rot, 3), word = rep(word, 3)) %>% head(N)
      
      posterior <- NULL
      while (typeof(posterior)=="NULL") {
       posterior <- webppl(model, 
                    data = input,
                    data_var = "input")
    }
      
      learning_norm <- posterior %>%
        rbindlist(idcol = TRUE) %>%
        gather(hypothese, prob, id:rotFrame_Side_ref) %>%
        dplyr::group_by(.id) %>%
        dplyr::mutate(prob = prob/sum(prob)) %>%
        dplyr::rename(word = .id) %>%
        dplyr::mutate(alpha = alpha,
                      beta = beta,
                      N = N)
      
      data_right_exp = bind_rows(data_right_exp, learning_norm)
      
    }
  }
}


data_front_exp = data.frame()

#Front/back
#############

x=c(0, -1, 0, 1)
y=c(1, 0, -1, 0)
rot=c(0, 90, 180, 270)
word=c('front', 'front', 'front', 'front')


for (alpha in alpha_val){
  for(beta in beta_val){
    for(N in N_val){
      
      input = data.frame(alpha = alpha, beta = beta, x= rep(x,3), y = rep(y,3), rot = rep(rot, 3), word = rep(word, 3)) %>% head(N)
      
      posterior <- NULL
      while (typeof(posterior)=="NULL") {
       posterior <- webppl(model, 
                    data = input,
                    data_var = "input")
    }
      
      learning_norm <- posterior %>%
        rbindlist(idcol = TRUE) %>%
        gather(hypothese, prob, id:rotFrame_Side_ref) %>%
        dplyr::group_by(.id) %>%
        dplyr::mutate(prob = prob/sum(prob)) %>%
        dplyr::rename(word = .id) %>%
        dplyr::mutate(alpha = alpha,
                      beta = beta,
                      N = N)
      
      data_front_exp = bind_rows(data_front_exp, learning_norm)
      
    }
  }
}



```



```{r}
alpha_val = c(1, 2, 4, 8, 16)
beta_val = c(1, 2, 4, 8, 16)
N_val = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12)

#Right/Left
#############

data_right = data.frame()

x=c(1, 0, -1, 0)
y=c(0, 1, 0, -1)
rot=c(0, 90, 180, 270)
word=c('right', 'right', 'right', 'right')

for (alpha in alpha_val){
  for(beta in beta_val){
    for(N in N_val){
      
      input = data.frame(alpha = alpha, beta = beta, x= rep(x,3), y = rep(y,3), rot = rep(rot, 3), word = rep(word, 3)) %>% head(N)
      
      posterior <- NULL
      while (typeof(posterior)=="NULL") {
       posterior <- webppl(model, 
                    data = input,
                    data_var = "input")
    }
      
      learning_norm <- posterior %>%
        rbindlist(idcol = TRUE) %>%
        gather(hypothese, prob, id:rotFrame_Side_ref) %>%
        dplyr::group_by(.id) %>%
        dplyr::mutate(prob = prob/sum(prob)) %>%
        dplyr::rename(word = .id) %>%
        dplyr::mutate(alpha = alpha,
                      beta = beta,
                      N = N)
      
      data_right = bind_rows(data_right, learning_norm)
      
    }
  }
}

data_front = data.frame()

#Front/back
#############

x=c(0, -1, 0, 1)
y=c(1, 0, -1, 0)
rot=c(0, 90, 180, 270)
word=c('front', 'front', 'front', 'front')


for (alpha in alpha_val){
  for(beta in beta_val){
    for(N in N_val){
      
      input = data.frame(alpha = alpha, beta = beta, x= rep(x,3), y = rep(y,3), rot = rep(rot, 3), word = rep(word, 3)) %>% head(N)
      
      posterior <- NULL
      while (typeof(posterior)=="NULL") {
       posterior <- webppl(model, 
                    data = input,
                    data_var = "input")
    }
      
      learning_norm <- posterior %>%
        rbindlist(idcol = TRUE) %>%
        gather(hypothese, prob, id:rotFrame_Side_ref) %>%
        dplyr::group_by(.id) %>%
        dplyr::mutate(prob = prob/sum(prob)) %>%
        dplyr::rename(word = .id) %>%
        dplyr::mutate(alpha = alpha,
                      beta = beta,
                      N = N)
      
      data_front = bind_rows(data_front, learning_norm)
      
    }
  }
}

```


```{r}

data_explore <- data_right_exp %>%
  filter(word == "right")#,
         #beta < alpha |  beta == alpha) 
  
  
data_explore$hypothese <- mapvalues(data_explore$hypothese, 
                                     from = c("id", "ref",  
                                              "rotSide_id","rotSide_ref",
                                              "rotFrame_id","rotFrame_ref",
                                              "rotFrame_Side_id","rotFrame_Side_ref"),
                                     to = c("front_ego", "back_ego", 
                                            "left_ego", "right_ego", 
                                            "front_allo", "back_allo", 
                                            "left_allo", "right_allo"))

data_explore$hypothese = factor(data_explore$hypothese, levels = c("front_ego", "back_ego", "left_ego", "right_ego", "front_allo", "back_allo", "left_allo", "right_allo"))

right_alpha2 <- ggplot(subset(data_explore, alpha==2), aes(x=hypothese, y=prob))+
  geom_col()+
  facet_grid(N  ~ beta) +
  theme(aspect.ratio = 0.7, axis.text.x = element_text(angle = 90, hjust = 1))


```

```{r}

data_explore <- data_front_exp %>%
  filter(word == "front")#,
         #beta < alpha |  beta == alpha) 
  
  
data_explore$hypothese <- mapvalues(data_explore$hypothese, 
                                     from = c("id", "ref",  
                                              "rotSide_id","rotSide_ref",
                                              "rotFrame_id","rotFrame_ref",
                                              "rotFrame_Side_id","rotFrame_Side_ref"),
                                     to = c("front_ego", "back_ego", 
                                            "left_ego", "right_ego", 
                                            "front_allo", "back_allo", 
                                            "left_allo", "right_allo"))

data_explore$hypothese = factor(data_explore$hypothese, levels = c("front_ego", "back_ego", "left_ego", "right_ego", "front_allo", "back_allo", "left_allo", "right_allo"))

front_alpha2 <- ggplot(subset(data_explore, alpha==2), aes(x=hypothese, y=prob))+
  geom_col()+
  facet_grid(N  ~ beta) +
  theme(aspect.ratio = 0.7, axis.text.x = element_text(angle = 90, hjust = 1))

front_alpha4 <- ggplot(subset(data_explore, alpha==4), aes(x=hypothese, y=prob))+
  geom_col()+
  facet_grid(N  ~ beta) +
  theme(aspect.ratio = 0.7, axis.text.x = element_text(angle = 90, hjust = 1))

front_alpha8 <- ggplot(subset(data_explore, alpha==8), aes(x=hypothese, y=prob))+
  geom_col()+
  facet_grid(N  ~ beta) +
  theme(aspect.ratio = 0.7, axis.text.x = element_text(angle = 90, hjust = 1))

front_alpha16 <- ggplot(subset(data_explore, alpha==16), aes(x=hypothese, y=prob))+
  geom_col()+
  facet_grid(N  ~ beta) +
  theme(aspect.ratio = 0.7, axis.text.x = element_text(angle = 90, hjust = 1))


```



Preliminary results
-We learn the egocentric representation before the allocentric representation (requires a relatively high value of beta)
-We learn the front-back representation before the left-right representation (because left-right is derived from front and back)
-The developmental data allows to combine the effect of input abd t

 
The data
```{r}

#Build training data, depending on what phenomenon we would like to investigate

#Input for "right"
x=c(1, 0, -1, 0)
y=c(0, 1, 0, -1)
rot=c(0, 90, 180, 270)
word=c('right', 'right', 'right', 'right')

right <- data.frame(x, y, rot, word)

#right <- data.frame(rep(x, 2), rep(y, 2), rep(rot, 2), rep(word, 2))


#Input to "front"
x=c(0, -1, 0, 1)
y=c(1, 0, -1, 0)
rot=c(0, 90, 180, 270)
word=c('front', 'front', 'front', 'front')

front <- data.frame(rep(x, 2), rep(y, 2), rep(rot, 2), rep(word, 2))
  
x = c(1, 1,-1,-1,1, -1, -1, -1,-1, -1, 1, 1,-1,-1,1, -1, -1, -1,-1, -1)
y = c(0, 0,0,0,0, 0, 0,0, 0,0, 0, 0,0,0,0, 0, 0,0, 0,0)
rot = c(0, 180, 180, 0, 0,0,0,0,0,0,0, 0,0,0,0, 0, 0,0, 0,0)
word= c('right', 'left', 'right', 'left', 'right', 'left', 'left','left','left','left',
        'left','left','left','left','left','left','left','left','left','left')

training = data.frame(x, y, rot, word)

training_1 <- head(training, 1)
training_2 <- head(training, 2)
training_3 <- head(training, 3)
training_4 <- head(training, 4)
training_5 <- head(training, 5)
training_6 <- head(training, 6)
training_7 <- head(training, 7)
training_8 <- head(training, 8)
training_9 <- head(training, 9)
training_10 <- head(training, 10)
training_11 <- head(training, 11)
training_12 <- head(training, 12)
training_13 <- head(training, 13)
training_14 <- head(training, 14)
training_15 <- head(training, 15)
training_16 <- head(training, 16)
training_17 <- head(training, 17)
training_18 <- head(training, 18)
training_19 <- head(training, 19)
training_20 <- head(training, 20)

```


```{r}

posterior <- webppl(model)
start = Sys.time()
posterior_1 <- webppl(model, 
                    data = training_1,
                    data_var = "training")
print(Sys.time() - start)

start = Sys.time()
posterior_2 <- webppl(model, 
                    data = training_2,
                    data_var = "training")
print(Sys.time() - start)

start = Sys.time()
posterior_3 <- webppl(model, 
                    data = training_3,
                    data_var = "training")
print(Sys.time() - start)

start = Sys.time()
posterior_4 <- webppl(model, 
                    data = training_4,
                    data_var = "training")
print(Sys.time() - start)

start = Sys.time()
posterior_5 <- webppl(model, 
                    data = training_5,
                    data_var = "training")
print(Sys.time() - start)

start = Sys.time()
 posterior_6 <- webppl(model, 
                     data = training_6,
                     data_var = "training")
 
print(Sys.time() - start)

start = Sys.time()
 posterior_7 <- webppl(model, 
                     data = training_7,
                     data_var = "training")
 
print(Sys.time() - start)

start = Sys.time()
 posterior_8 <- webppl(model, 
                     data = training_8,
                     data_var = "training")
 
print(Sys.time() - start)
 
start = Sys.time()
 posterior_9 <- webppl(model, 
                     data = training_9,
                     data_var = "training")
 
print(Sys.time() - start)

start = Sys.time()
 posterior_10 <- webppl(model, 
                     data = training_10,
                     data_var = "training")
 
print(Sys.time() - start)

start = Sys.time()
posterior_11 <- webppl(model, 
                    data = training_11,
                    data_var = "training")
print(Sys.time() - start)

start = Sys.time()
posterior_12 <- webppl(model, 
                    data = training_12,
                    data_var = "training")
print(Sys.time() - start)

start = Sys.time()
posterior_13 <- webppl(model, 
                    data = training_13,
                    data_var = "training")
print(Sys.time() - start)

start = Sys.time()
posterior_14 <- webppl(model, 
                    data = training_14,
                    data_var = "training")
print(Sys.time() - start)

start = Sys.time()
posterior_15 <- webppl(model, 
                    data = training_15,
                    data_var = "training")
print(Sys.time() - start)

start = Sys.time()
 posterior_16 <- webppl(model, 
                     data = training_16,
                     data_var = "training")
 
print(Sys.time() - start)

start = Sys.time()
 posterior_17 <- webppl(model, 
                     data = training_17,
                     data_var = "training")
 
print(Sys.time() - start)

start = Sys.time()
 posterior_18 <- webppl(model, 
                     data = training_18,
                     data_var = "training")
 
print(Sys.time() - start)
 
start = Sys.time()
 posterior_19 <- webppl(model, 
                     data = training_19,
                     data_var = "training")
 
print(Sys.time() - start)

start = Sys.time()
 posterior_20 <- webppl(model, 
                     data = training_20,
                     data_var = "training")
 
print(Sys.time() - start)

iter1 <- posterior_1[which.max(posterior_1$prob),]
iter2 <- posterior_2[which.max(posterior_2$prob),]
iter3 <- posterior_3[which.max(posterior_3$prob),]
iter4 <- posterior_4[which.max(posterior_4$prob),]
iter5 <- posterior_5[which.max(posterior_5$prob),]
iter6 <- posterior_6[which.max(posterior_6$prob),]


```


Get data 
```{r}
#split by word
#split by hypothese
#Normalize by sclae 

#iterations = list(posterior_1, posterior_2, posterior_3, posterior_4, posterior_5, posterior_6)
iterations = list(iter1, iter2, iter3, iter4, iter5, iter6)
learning = data.frame()


for (i in 1:length(iterations)) {

left <- iterations[[i]] %>%
  dplyr::select(starts_with("left")) %>%
  gather(hypothese, prob) %>%
  dplyr::mutate(hypothese = gsub("left.", "", hypothese )) %>%
  dplyr::mutate(word  = "left")

right <- iterations[[i]] %>%
  dplyr::select(starts_with("right")) %>%
  gather(hypothese, prob) %>%
  dplyr::mutate(hypothese = gsub("right.", "", hypothese )) %>%
  dplyr::mutate(word  = "right")

lexicon = bind_rows(left, right) %>%
  mutate(iteration = i)
  
  learning =  bind_rows(learning, lexicon)
  
}

learning_norm <- learning %>%
  dplyr::group_by(iteration, word) %>%
  dplyr::mutate(prob = prob/sum(prob))

#Reorder the hypotheses for the plot


learning_norm$hypothese <- mapvalues(learning_norm$hypothese, from = c("rotSide_id","rotSide_ref","rotFrame_Side_id","rotFrame_Side_ref"), to = c("left_ego", "right_ego", "left_allo", "right_allo"))

learning_norm$hypothese = factor(learning_norm$hypothese, levels = c("left_ego", "right_ego", "left_allo", "right_allo"))

ggplot(learning_norm, aes(x=hypothese, y=prob))+
  geom_col()+
  facet_grid(word ~ iteration) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


